Topic modeling bla bla

### 2017-06-05 thesis_report/draft_thesis.tex
Edit: LDA model

\usepackage{amsfonts}
\usepackage{graphicx}

@@

\subsection{The Multinomial Distribution}
Once we have a representation for individual documents, the natural next step
is to select a model for a set of documents. It is important to understand the
difference between a representation and a model. A representation is a way of
encoding an entity as a data structure. A model is an abstraction of a set of
entities, for example a probability distribution. Given a training set of
documents, we will choose values for the parameters of a probabilistic model
that make the training documents have high probability. Then, given a test
document, we can evaluate its probability according to the model. The higher
this probability is, the more similar the test document is to the training set.

@@

@@

>>>>

\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{biblatex}
\addbibresource{sample.bib}

@@

\subsection{The Multinomial Distribution}

Once we have a representation for individual documents, the natural next step
is to select a model for a set of documents. It is important to understand the
difference between a representation and a model. A representation is a way of
encoding an entity as a data structure. A model is an abstraction of a set of
entities, for example a probability distribution. Given a training set of
documents, we will choose values for the parameters of a probabilistic model
that make the training documents have high probability. Then, given a test
document, we can evaluate its probability according to the model. The higher
this probability is, the more similar the test document is to the training set.

@@

LDA is a probabilistic model of text documents, which assumes a collection of 
K topics. Each topic defines a multinomial distribution over the vocabulary 
and is assumed to have been drawn from a Dirichlet 
$\beta_k \sim Dirichlet(\eta)$.

@@

We can analyze a corpus of documents with LDA by examining the posterior 
distribution of topics $\beta$, topic proportions $\theta$ and topic 
assignments $z$ conditioned on the documents. This reveals latent structure 
in the collection that can be used for prediction or data exploration. This 
posterior can't be computed directly; it is usually approximated using Markov 
Chain Monte Carlo (MCMC) or variational inference. Both methods are effective, 
but also present significant computational challenges in large data sets \cite{onlineLDAvb}. In our implementation, we're using the online variational 
LDA model, which is described in section 2.2.3.4.
